On proving things

### 2015-10-16 reasoning/huiswerk/inl1019.tex
finshed all of 2 I think....

\subsubsection{$R\neg$}
Suppose C occurs positively the premiss
($\Gamma, A \Rightarrow \Delta$). Thus it occurs positively in a formula
in $\Delta$ or negatively in a formula in $\Gamma$ or $A$.
In the first and the last case,
the same holds for the conclusion ($\Gamma \Rightarrow \neg A, \Delta$).
In case C occurs negatively in $A$ then by definition it occurs negatively
in $\neg A$ (even in the case that $C = A$). Hence it occurs negatively
in ($\Gamma \Rightarrow \neg A, \Delta$). This is what had to be shown.
\subsection{Proof introduction of $A\wedge B$ remains positive}
\end{document}

>>>>

\subsubsection{$R\neg$}
Suppose C occurs positively the premiss
($\Gamma, A \Rightarrow \Delta$). Thus it occurs positively in a formula
in $\Delta$ or negatively in a formula in $\Gamma$ or $A$.
In the first and the last case,
the same holds for the conclusion ($\Gamma \Rightarrow \neg A, \Delta$).
In case C occurs negatively in $A$ then by definition it occurs negatively
in $\neg A$ (even in the case that $C = A$). Hence it occurs negatively
in ($\Gamma \Rightarrow \neg A, \Delta$). This is what had to be shown.

\subsection{Proof introduction remains positive}

\subsubsection{$A\wedge B$}
To prove that in any proof in GKC of a sequent $S$, if the formula
$A \wedge B$ is introduced in an application of the $R\wedge$ rule,
then that $A \wedge B$ occurs positively in the endsequent $S$of the
proof.

Let $A \wedge B$ be C, as shown in 2.1 if formula C occurs positively in
one of the premises of a rule, then the same formula occurs positively in
the conclusion for all rules of GKC, now we have proven that C will
occur in the endsequent.

\subsubsection{$A\vee B$}
To prove that in any proof in GKC of a sequent $S$, if the formula
$A \vee B$ is introduced in an application of the $R\vee$ rule,
then that $A \vee B$ occurs positively in the endsequent $S$of the
proof.

Let $A \vee B$ be C, as shown in 2.1 if formula C occurs positively in
one of the premises of a rule, then the same formula occurs positively in
the conclusion for all rules of GKC, now we have proven that C will
occur in the endsequent.

\subsection{Single branch}
To prove that every provable sequent that does not contains negations and
implications and in which every subformula of the form $A \wedge B$ occurs
negatively and every subformula of the form $A \vee B$ occurs positively,
has a proof in GKC that consists of a single branch.

Because the sequent does not contain negations and implications the rules
$R\to$, $L\to$, $R\neg$ and $L\neg$ can't be applied.
$R\wedge$ can't be applied because $A \wedge B$ occurs negatively,
which by definition means $A \wedge B$ occurs on the $L$ side of the
$\wedge$ rules.
$L\vee$ can't be
applied because $A \vee B$ occurs positively, which by definition means
that the $A \vee B$ formula is on the $R$ side of the $\vee$ rules.

The only applicable rules left in GKC are the $L\wedge$ and $R\vee$ rules.
These are single branch by definition. Thus this entire proof has a single
branch, this is what had to be shown.

\subsection{$S$ consists of \ldots}
Supose that $S$ is a provable sequent that does not contain negations and
implications and which every subformula of the form $A\wedge B$ occurs
negatively and every subformula of the form $A \vee B$ occurs positively.
Show that if the sum of all the occurrences of connectives in $S$ is $n$.
then $S$ has a proof in $GKC$ that consists of at most $n + 1$ sequents.

Because the sequent $S$ does not contain negations and implications the rules
$R\to$, $L\to$, $R\neg$ and $L\neg$ can't be applied.
$R\wedge$ can't be applied because $A \wedge B$ occurs negatively,
which by definition means $A \wedge B$ occurs on the $L$ side of the
$\wedge$ rules.
$L\vee$ can't be
applied because $A \vee B$ occurs positively, which by definition means
that the $A \vee B$ formula is on the $R$ side of the $\vee$ rules.

The only applicable rules left in GKC are the $L\wedge$ and $R\vee$ rules.
Both the $L\wedge$ and $R\vee$ rules add only 1 connective to the conclusion
once applied to the premise, creating a new sequent in the process. The proof
of $S$ also has just a single branch, because $L\wedge$ and $R\vee$ only allow
a single premise.
So the
sequent count in the proof of $S$ is at least $n$. It is $n$ + 1 because $S$ is also
a sequent by definition. This is what had to be shown.
\end{document}
